### 2017-06-05 Conclusion/Conclusion.tex
Corrections

The search for a heavy Higgs boson decaying to a final state of $\Pbottom\Pbottom\Pgt\Pgt$ via two
$125\,\GeV$ Higgs bosons was performed using $19.7\,\invfb$ of data collected at a
centre-of mass energy of $8\,\TeV$ during the 2012 \ac{LHC} data-taking period. Such a final
state can access areas of the \ac{MSSM} parameter space not easily accessible via other channels.
To separate more signal-like and more background-like events, a categorisation based on the number of 
b-tagged jets is used. To further increase the sensitivity to the signal, cuts on the di-tau and di-jet
mass in a window around $125\,\GeV$ are used in combination with a kinematic fitting technique for
the reconstruction of the four-body mass.
The resulting mass variable provides good separation between the signal and the dominant
\ttbar background, and is thus used as the variable for signal extraction. 
The results of this search are upper limits on production cross section times branching 
ratio, in a mass range of $260<m_{\PHiggs}<350\,\GeV$. A combination with a search for \AtoZhtolltautau
yields exclusion in the lowest \tanb~region of the low-\tanb~\ac{MSSM} scenario, as well
as several areas of the \cosba-\tanb~plane in a \ac{2HDM} scenario \cite{CMS-HIG-14-034}.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.7\textwidth]{./Conclusion/Figures/scenario_comp2.pdf}
\end{center}
\caption[The expected exclusion in the $m_{\PHiggslight}^{\text{mod+}}$ scenario
at the 95\% CL of the 2015 MSSM analysis, projected to integrated luminosities of $300$ and $3000\,\invfb$.]{The expected exclusion in the $m_{\PHiggslight}^{\text{mod+}}$ scenario
 at the 95\% CL of the 2015 MSSM analysis (pink)
projected to integrated luminosities of $300\,\invfb$ (blue) and $3000\,\invfb$ (red)
under several assumptions of how the systematic uncertainties scale. In scenario ``S1''
all systematic uncertainties are kept constant with integrated luminosity, while in scenario ``S2'' 
the theoretial uncertainties are scaled down by a factor $\frac{1}{2}$ and experimental
systematic uncertainties scale down by the square root of the integrated luminosity until they reach
a lower limit. In the ``Stat. Only'' scenario all systematic uncertainties are neglected. Even with an integrated 
luminosity of $3000\,\invfb$ it is not possible to exclude the entire \mA-\tanb~plane
in this \ac{MSSM} benchmark scenario using this analysis alone \cite{HTT-projection}.}
\label{fig:mssm_projection_fig}
\end{figure}

>>>>

The search for a heavy Higgs boson decaying to a final state of $\Pbottom\Pbottom\Pgt\Pgt$ via two
$125\,\GeV$ Higgs bosons was performed using $19.7\,\invfb$ of data collected at a
centre-of-mass energy of $8\,\TeV$ during the 2012 \ac{LHC} data-taking period. Such a final
state can access areas of the \ac{MSSM} parameter space not easily accessible via other channels.
To separate more signal-like and more background-like events, a categorisation based on the number of 
b-tagged jets is used. To further increase the sensitivity to the signal, cuts on the di-tau and di-jet
mass in a window around $125\,\GeV$ are used in combination with a kinematic fitting technique for
the reconstruction of the four-body mass.
The resulting mass variable provides good separation between the signal and the dominant
\ttbar background, and is thus used as the variable for signal extraction. 
The results of this search are upper limits on production cross section times branching 
ratio, in a mass range of $260<m_{\PHiggs}<350\,\GeV$. A combination with a search for \AtoZhtolltautau
yields exclusion in the lowest \tanb~region of the low-\tanb~\ac{MSSM} scenario, as well
as several areas of the \cosba-\tanb~plane in a \ac{2HDM} scenario \cite{CMS-HIG-14-034}.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.7\textwidth]{./Conclusion/Figures/scenario_comp2.pdf}
\end{center}
\caption[The expected exclusion in the $m_{\PHiggslight}^{\text{mod+}}$ scenario
at the 95\% CL of the 2015 MSSM analysis, projected to integrated luminosities of $300$ and $3000\,\invfb$.]{The expected exclusion in the $m_{\PHiggslight}^{\text{mod+}}$ scenario
 at the 95\% CL of the 2015 MSSM analysis (pink)
projected to integrated luminosities of $300\,\invfb$ (blue) and $3000\,\invfb$ (red)
under several assumptions of how the systematic uncertainties scale. In scenario ``S1''
all systematic uncertainties are kept constant with integrated luminosity, while in scenario ``S2'' 
the theoretial uncertainties are scaled down by a factor $\frac{1}{2}$ and experimental
systematic uncertainties scaled down by the square root of the integrated luminosity until they reach
a lower limit. In the ``Stat. Only'' scenario all systematic uncertainties are neglected. Even with an integrated 
luminosity of $3000\,\invfb$ it is not possible to exclude the entire \mA-\tanb~plane
in this \ac{MSSM} benchmark scenario using this analysis alone \cite{HTT-projection}.}
\label{fig:mssm_projection_fig}
\end{figure}

### 2017-06-05 Detector/Detector.tex
Corrections

The pixel tracker will be upgraded during the extended year-end technical stop in late 2016-early 2017. This upgrade is needed to
maintain the performance of the tracker as the pileup increases over the next few years \cite{cms-pixel-upgrade}. %or just replaced?

@@

The energy resolution of the \ac{ECAL} can be parameterised as
\begin{equation}\label{eqn:ecalres}
\frac{\sigma}{E} = \frac{S}{\sqrt{E}}\oplus\frac{N}{E}\oplus C,
\end{equation}
where $S$ is the stochastic term, $N$ the noise term and $C$ the constant term.
The stochastic term arises from fluctuations in lateral shower containment and 
fluctuations in the scintillation yield, the noise term is due to noise from the electronics
and additional particles in the event, and the constant term comes
from calibration errors and the non-uniformity of the longitudinal response.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.7\textwidth]{./Detector/Plots/CMSTrigger.png}
\caption[Schematic of the different components of the L1 trigger.]{Schematic of the different components of the \ac{L1} trigger \cite{cms-trigger-tdr}.}
\label{fig:CMS_Trigger}
\end{center}
\end{figure}

>>>>

The pixel tracker was upgraded during the extended year-end technical stop in late 2016-early 2017. This upgrade was needed to
maintain the performance of the tracker as the pileup increases throughout the remainder of Run 2 \cite{cms-pixel-upgrade}. %or just replaced?

@@

The energy resolution of the \ac{ECAL} can be parameterised as
\begin{equation}\label{eqn:ecalres}
\frac{\sigma}{E} = \frac{S}{\sqrt{E}}\oplus\frac{N}{E}\oplus C,
\end{equation}
where $S$ is the stochastic term, $N$ the noise term and $C$ the constant term.
The stochastic term arises from fluctuations in lateral shower containment and 
fluctuations in the scintillation yield, the noise term is due to noise from the electronics
and additional particles in the event, and the constant term comes
from crystal-to-crystal intercalibration errors, the non-uniformity of the longitudinal response and 
energy leakage from the back of the crystals.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=\textwidth]{./Detector/Plots/CMSTrigger.png}
\caption[Schematic of the different components of the L1 trigger.]{Schematic of the different components of the \ac{L1} trigger \cite{cms-trigger-tdr}.}
\label{fig:CMS_Trigger}
\end{center}
\end{figure}
